Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-09 minimax.tex
Related works (minor)

\Citet{Konczak05} were the first to consider the problem of computing, for various voting rules, possible and necessary winners in the case of partial knowledge of agent preferences and showed that the problem is hard in the general case.
This work was then extended by \citet{Xia2008} that showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard (the authors found a mistake in a proof in the Konczak and Lang's paper that claimed it to be polynomial); they also  proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}.
In other papers it was showed that the general case remains computationally hard even when restricting to single-peaked preferences \citep{Walsh2007};  sufficient conditions that ensure tractability were then found \citep{Pini2007}.

@@

Thereafter, noticing that in many practical situations there would be too many possible winners but no necessary winners, the importance of proposing efficient elicitation strategies has been identified. 
Indeeed, several works addressed the problem of  elicitation of agent preferences \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2} using a variety of approaches (minimax regret, Bayesian methods, etc.), and analysis on when to stop the elicitation process \citep{Walsh2009,Conitzer2009}.

@@

More recently \citet{Llamazares2013} and \cite{Viappiani2018} (among others) considered the problem of dealing with unspecified weights in positional scoring rules; the first  \citep{Llamazares2013} proposed a method based on Data Envelope Analysis, while the second \citep{Viappiani2018} proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret). 
We also mention the work of \citet{Cailloux2014} that deals with the problem of eliciting a generic voting rule.

>>>>

\Citet{Konczak05} were the first to consider the problem of computing, for various voting rules, possible and necessary winners in the case of partial knowledge of agent preferences and showed that the problem is hard in the general case.
This work was then extended by \citet{Xia2008} that showed that, while the identification of a necessary co-winner in scoring rules is polynomial,  the determination of possible co-winners is NP-hard; they also  proposed polynomial-time algorithms when using maximin and Bucklin \citep{Xia2008}.
In other papers it was showed that the general case remains computationally hard even when restricting to single-peaked preferences \citep{Walsh2007};  sufficient conditions that ensure tractability were then found \citep{Pini2007}.

@@

Thereafter, noticing that in many practical situations there would be too many possible winners but no necessary winners, the importance of proposing efficient elicitation strategies has been identified. 
Several works addressed the problem of  elicitation of agent preferences \citep{Naamani-Dery2015,Kalech2011,Lu2011,Pini2009,Benabbou2016,Dey2016,Dey2016_2} using a variety of approaches (minimax regret, Bayesian methods, etc.), and others \citep{Walsh2009,Conitzer2009}  analyzed when to stop the elicitation process.

@@

More recently \citet{Llamazares2013} and \citet{Viappiani2018} (among others \commentOC{Which others?}) considered the problem of dealing with unspecified weights in positional scoring rules; the first \citep{Llamazares2013} proposed a method based on Data Envelope Analysis, while the second \citep{Viappiani2018} proposed to aggregate the uncertainty in weights using criteria used in decision-making under uncertainty (such as minimax regret). 
The work of \citet{Cailloux2014} deals with the problem of eliciting a generic voting rule.
